An open reproducible framework for the study of the iterated prisoner's dilemma

### 2016-04-01 tex/paper.tex
Swapping citation order.
Using jors style file.
Adding Kristian (my bad for forgetting).
Conflicts:
	tex/paper.pdf
Revert "Using jors style file."
This reverts commit 9d71034ace5ec1638b0d8982492c8b965cb3da5a.

Conflicts:
	tex/paper.pdf
Correct first two section names as per JORS.

% All devs (alphabetic order of last name)
\author[2]{James Campbell}
\author[5]{Thomas Campbell}
\author[2]{Alex Carney}
\author[2]{Martin Chorley}
\author[1]{Cameron Davidson-Pilon}
\author[1]{Tom{\'a}{\v s} Ehrlich}
\author[1]{Martin Jones}
\author[4]{Georgios Koutsovoulos}
\author[1]{Holly Marissa}
\author[1]{Jochen M{\"u}ller}
\author[2]{Geraint Palmer}
\author[3]{Paul Slavin}
\author[2]{Timothy Standen}
\author[1]{Luis Visintini}
\author[1]{Karl ?}

@@

\section{Introduction}\label{sec:introduction}

@@

@@

As stated in Section~\ref{sec:introduction}, one of the main goals of the library
is to allow for the easy contribution of strategies. Doing this requires the
writing of a simple Python class (which can inherit from other predefined
classes). Full contribution guidelines can be found in the documentation.
As an example, Figures~\ref{fig:grudger} and~\ref{fig:grudger_test} show the source code for
the Grudger strategy as well as its corresponding test.

@@

\section{New strategies, tournaments and implications}\label{sec:new-strategies-and-implications}

@@

The example of (\ref{equ:example_of_lookerup}) is an incomplete illustration of
the mapping for \(m=8, n=2\). Intuitively, this state space uses the initial
plays of the opponent to gain some information about its intentions whilst still
taking into account the recent play. The actual winning strategy is an instance
of the framework for \(m=n=2\) for which a particle swarm algorithm has been
used to train it, the second placed strategy was trained with an evolutionary
algorithms. More details of this can be found in \cite{Goerge2016, Jones2015}.
In \cite{Knight2015} experiments are described that evaluate how the second
placed strategy behaves in environments other than those in which it was trained
and it continues to perform strongly.

>>>>

% All devs (alphabetic order of last name)
\author[2]{James Campbell}
\author[5]{Thomas Campbell}
\author[2]{Alex Carney}
\author[2]{Martin Chorley}
\author[1]{Cameron Davidson-Pilon}
\author[1]{Kristian Glass}
\author[1]{Tom{\'a}{\v s} Ehrlich}
\author[1]{Martin Jones}
\author[4]{Georgios Koutsovoulos}
\author[1]{Holly Marissa}
\author[1]{Jochen M{\"u}ller}
\author[2]{Geraint Palmer}
\author[3]{Paul Slavin}
\author[2]{Timothy Standen}
\author[1]{Luis Visintini}
\author[1]{Karl ?}

@@

\section{Overview}\label{sec:sec:overview}

@@

\section{Implementation and architecture}

@@

As stated in Section~\ref{sec:sec:overview}, one of the main goals of the library
is to allow for the easy contribution of strategies. Doing this requires the
writing of a simple Python class (which can inherit from other predefined
classes). Full contribution guidelines can be found in the documentation.
As an example, Figures~\ref{fig:grudger} and~\ref{fig:grudger_test} show the source code for
the Grudger strategy as well as its corresponding test.

@@

\subsection{New strategies, tournaments and implications}\label{sec:new-strategies-and-implications}

@@

The example of (\ref{equ:example_of_lookerup}) is an incomplete illustration of
the mapping for \(m=8, n=2\). Intuitively, this state space uses the initial
plays of the opponent to gain some information about its intentions whilst still
taking into account the recent play. The actual winning strategy is an instance
of the framework for \(m=n=2\) for which a particle swarm algorithm has been
used to train it, the second placed strategy was trained with an evolutionary
algorithms. More details of this can be found in \cite{Jones2015, George2016}.
In \cite{Knight2015} experiments are described that evaluate how the second
placed strategy behaves in environments other than those in which it was trained
and it continues to perform strongly.
